Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-01 Paper/grass.tex

\begin{figure}
\includegraphics[scale=1]{Grass_Base_Vivoni_shear}
\caption{Steady flow profile from the experiment of XX\cite{XX} (Case-XXXX from Figure-XX with XX plants/$m^2$, XX blades per plant, 
plant height = XX$\pm XX$ and blade width of XX cm)
 and it's approximation with $U_0=XX$ cm/s and $\delta = 0.2H$ with our model. The canopy extends upto $y=h_g$ in the water column of depth $3H$. The steady velocity profile can be decomposed into three regions, (i) A parabolic profile in the unvegetated region, (ii) a uniform profile deep within the grass bed, and (iii) a boundary layer of thicness $\delta$ near the canopy top. The depedence of the boundary layer on the vegetation density $\Ndg$ is shown in the inset.}
\label{fig:basicflow}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[]{Critical_Re_vs_delta_noshear} \\
\vspace{-6mm} \hspace{-3mm}
\includegraphics[]{K_vs_shear_width_noshear}
\end{center}
\caption{Critical Reynolds number with flow (top) and the corresponding marginally stable wave number (bottom) for different submergence ratios as a function of vegetation density parametrized by the boundary layer thickness. Parameters estimated from experiments reported by Ghisalberti and Nepf\cite{Ghisal02} to exhibit or suppress synchronous waving are also included in the top panel. In order to estimate the $\Rey$ for these experiments, a representative value of $\mu=0.1$ Pa~s was assumed. Inset compares experimental observations of the dominant frequency $f_o$ (in Hz?) measured with the predictions from the solution of \eqref{Orr-somerfield}. The experimental data in the inset in obtained from the articles by XX\cite{} and XX\cite{}.}
\label{Re_vs_delta}
\end{figure}
We use a mean field model for the coupling between the flow and the canopy. 
Drag force exerted by the grass is approximated via a continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$ in the fluid momentum balance\cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06} as
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}, \quad \grad\cdot\bu = 0,
\label{navier-stokes}
\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of the grass blade, $N_g$ the grass number density per unit area, $\rho$ the fluid density, $\mathbf{u}$ the velocity, 
$P$ the pressure, $\mu$ the turbulent viscosity and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow on the scale of a grass blade is expected to be O($10^2$-$10^3$), and hence the drag force is dominated by form drag, and is modeled as $\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn + C_{T}\rho u_{T}^{2}d\bt$ \shreyas{citation needed} where $d$ is average width of grass blade $C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively; $\bu_{T}$, $\bu_{N}$ are velocity vector along and
normal to grass while $\bt,\bn$ being unit vector along and normal to grass. 
We expect $C_T \ll C_N$ and take $C_T=0$ for rest of analysis. 
In the field, both $C_N$ and $N_g$ vary with distance from the bottom but we do not expect these variation to be central to the mechanism and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments\cite{Vivoni98}, we take $C_N \approx 1$.

>>>>

\begin{figure}
\includegraphics[scale=1]{Grass_Base_Nepf_shear}
\caption{Steady flow profile from the experiment of Ghisalberti\cite{Nepf04} (Case-I from Table-1 with 1250 plants/$m^2$, 
plant height = 13.7$\pm .2$cm and blade width of 0.64 cm)
 and it's approximation with $U_0=7.28$ cm/s and $\delta = 5.02$ cm with our model. The canopy extends upto $y=h_g$ in the water column of depth $2H$. 
The steady velocity profile can be decomposed into three regions, (i) A parabolic profile in the unvegetated region, (ii) a uniform profile deep within the grass bed, and (iii) a boundary layer of thicness $\delta$ near the canopy top. The depedence of the boundary layer on the vegetation density $\Ndg$ is shown in the inset and compared with our prediction.}
\label{fig:basicflow}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[]{Critical_Re_vs_delta_noshear} \\
\vspace{-6mm} \hspace{-3mm}
\includegraphics[]{K_vs_shear_width_noshear}
\end{center}
\caption{Critical Reynolds number with flow (top) and the corresponding marginally stable wave number (bottom) for different submergence ratio as a function of vegetation density
 parametrized by the boundary layer thickness. Parameters estimated from experiments reported by Ghisalberti and Nepf\cite{Ghisal02} to exhibit or suppress synchronous waving are 
also included in the top panel. In order to estimate the $\Rey$ for these experiments, a representative value of $\mu=0.1$ Pa~s was assumed. Inset compares experimental observations 
of the dominant frequency $f_o$ (in Hz) measured with the predictions from the solution of \eqref{Orr-somerfield}. The experimental data in the inset in obtained from the articles by 
Ghisalberti \cite{Ghisal02} and Vivoni \cite{Vivoni98}.}
\label{Re_vs_delta}
\end{figure}
We use a mean field model for the coupling between the flow and the canopy. 
Drag force exerted by the grass is approximated via a continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$ in the fluid momentum balance\cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06} as
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}, \quad \grad\cdot\bu = 0,
\label{navier-stokes}
\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of the grass blade, $N_g$ the grass number density per unit area, $\rho$ the fluid density, $\mathbf{u}$ the velocity, 
$P$ the pressure, $\mu$ the turbulent viscosity and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow on the scale of a grass blade is expected to be O($10^2$-$10^3$), and hence the drag force is dominated by form drag, and is modeled as $\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn + C_{T}\rho u_{T}^{2}d\bt$ \shreyas{citation needed} where $d$ is average width of grass blade $C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively; $\bu_{T}$, $\bu_{N}$ are velocity vector along and
normal to grass while $\bt,\bn$ being unit vector along and normal to grass. 
We expect $C_T \ll C_N$ and take $C_T=0$ for rest of analysis. 
In the field, both $C_N$ and $N_g$ vary with distance from the bottom but we do not expect these variation to be central to the mechanism and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments\cite{Vivoni98}, we take $C_N \approx 1$.
